---
 title       : My presentation
 author      : Kirill Zhuravlev  
 framework   : revealjs  
 highlighter : highlight.js
 hitheme     : default  
 widgets     : []    
 mode        : selfcontained 
 knit        : slidify::knit2slides
---

## Car efficiency prediction

<br>
<br>
</br>
  Author Kirill Zhuravlev
  
<br>
<br>
</br>
  
  Course Developing Data Products
  
<br>
<br>
</br>
  
  Done: 2016

---

## Importance of the problem

<br>
<br>
</br>
 - Car efficiency prediction is important for several groups of people:
 - 1) Self-employed (pizza delivery, newspaper delivery, babysitters, tutors etc.)
 - 2) Frequent travelers (salespersons, advertisers)
 - 3) Small businesses (fast-food, pet grooming, carpet/house cleaning, yard/lawn management, etc.)

---

## Importance of the problem (cont.)

<br>
<br>
</br>
 - Costs of fuel are important in planning and managing business, may constitute significant portion of costs
 - How efficient is the car you or your business use? Can we predict it based on its power?
 - Does efficiency depend on the transmission type of your vehicle?
 - We present new algorithm allowing one to predict the car fuel        consumption efficiency (measured in miles per gallon of fuel) if the car power and its transmission type are given.

---

### Data used to build the prediction model

```{r, echo=FALSE, fig.align='center', warning=FALSE}
data(mtcars)
library(ggplot2)
g<-ggplot(mtcars, aes(x=hp, y=mpg))
g<-g+geom_boxplot(aes(color=factor(am)))+labs(x="Power, hp", y="Efficiency, mpg", color="Transmission type")
g
#t.test(subset(mtcars, mtcars$am==0)$mpg, subset(mtcars, #mtcars$am==1)$mpg, mu=0)$p.value
```
P-value is 0.0013, showing the statistical significance of the difference between two types of transmission.

---

### Data with the linear regression models

```{r, echo=FALSE, fig.align='center'}
data(mtcars)
library(ggplot2)
fit0<-lm(mpg~hp, subset(mtcars, mtcars$am==0))
fit1<-lm(mpg~hp, subset(mtcars, mtcars$am==1))
g <- ggplot(mtcars, aes(x = hp, y = mpg))
g <- g  + scale_size(range = c(10, 45), guide = "none" )
g <- g + geom_point(aes(color=factor(am)), size=5)+labs(x="Power, hp", y="Efficiency, mpg", color="Transmission type")
g <- g+geom_abline(intercept=coef(fit1)[1], slope=coef(fit1)[2], size=2, color="blue")
g<-g+geom_abline(intercept=coef(fit0)[1], slope=coef(fit0)[2], size=2, color="red")
g
```
Blue and red lines are best linear fits for cars with manual and automatic transmission, respectively.

---

### Web application done using shiny

<br>
<br>
</br>
Data was taken from 1974 Motor Trend US magazine. We used simple linear regression model to predict the efficiency of a vehicle based on its power, measured in horsepowers.
<br>
<br>
</br>
Link to application:
https://kzhuravlev.shinyapps.io/My_data_product_project/

