---
title       : Car efficiency prediction
subtitle    : 
author      : Kirill Zhuravlev  
job         : Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Importance of the problem

 - Car efficiency prediction is important for several groups of people:
 - 1) Self-employed (pizza delivery, newspaper delivery, babysitters, tutors etc.)
 - 2) Frequent travelers (salespersons, advertisers)
 - 3) Small businesses (fast-food, pet grooming, carpet/house cleaning, yard/lawn management, etc.)
 - Costs of fuel are important in planning and managing business, may constitute significant portion of costs
 - How efficient is the car you or your business use? Can we predict it based on its power?
 - Does efficiency depend on the transmission type of your vehicle?
 - We present new algorithm allowing one to predict the car fuel        consumption efficiency (measured in miles per gallon of fuel) if the car power and its transmission type are given.

---

## Data used to build the prediction model

```{r, echo=FALSE, fig.align='center'}
data(mtcars)
library(ggplot2)
g <- ggplot(mtcars, aes(x = hp, y = mpg))
g <- g  + scale_size(range = c(10, 45), guide = "none" )
g <- g + geom_point(aes(color=factor(am)), size=5)+labs(x="Power, hp", y="Efficiency, mpg", color="Transmission type")
g
```
Data was taken from 1974 Motor Trend US magazine. We used simple linear regression model to predict the efficiency of a vehicle based on its power, measured in horsepowers.

---

## Data with the linear regression models

```{r, echo=FALSE, fig.align='center'}
data(mtcars)
library(ggplot2)
fit0<-lm(mpg~hp, subset(mtcars, mtcars$am==0))
fit1<-lm(mpg~hp, subset(mtcars, mtcars$am==1))
g <- ggplot(mtcars, aes(x = hp, y = mpg))
g <- g  + scale_size(range = c(10, 45), guide = "none" )
g <- g + geom_point(aes(color=factor(am)), size=5)+labs(x="Power, hp", y="Efficiency, mpg", color="Transmission type")
g <- g+geom_abline(intercept=coef(fit1)[1], slope=coef(fit1)[2], size=2, color="blue")
g<-g+geom_abline(intercept=coef(fit0)[1], slope=coef(fit0)[2], size=2, color="red")
g
```
Blue and red lines are best linear fits for cars with manual and automatic transmission, respectively.

---

## Web application done using shiny

Below is a screenshot of our web application
```{r, message=FALSE, echo=FALSE, cache=FALSE}
library(shiny)
library(UsingR)
shinyUI(fluidPage(
  titlePanel(strong("Car efficiency calculator", style="color:red")),
  
  sidebarLayout(
    sidebarPanel(
      numericInput('hrp', p('Power, hp', style="color:orange"), 100, min=0, max=400),
      br(),
      radioButtons(inputId="trans", label =p(em('Transmission type', style="color:magenta")), 
                   choices=list("Automatic"="auto", "Manual"="man")),
      submitButton("Submit")
    ),
    
    mainPanel(
     h3("Your car efficiency is", style="color:blue"),
      textOutput("hrp", inline=TRUE),
       h5(strong("mpg"))
  )
 )
))
runApp(display.mode = "showcase")
```
